### 2024-02-29 presentation/parts/introduction.tex
WIP

>>>>

\tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
\tikzstyle{myrect} = [fill]

\begin{frame}
    \frametitle{Building a decision-support system}
    \begin{columns}
        \begin{column}{0.6\textwidth}
            Modular approach:
            \begin{itemize}
                \item \highlight{Input}: Speech or text (potentially video, tabular data, images, etc.).
                \item \highlight{Parsing the input}: Representation learning and speech recognition.
                \item \highlight{Output}: Predictions (suggesting, summarizing, classifying, etc.).
            \end{itemize}
        \end{column}
        \begin{column}{0.4\textwidth}
            \resizebox{!}{0.8\textheight}{%
            \begin{tikzpicture}[x=1cm,y=1cm]
                \node<6> [mybox, fill=presentation_orange] at (0,5) (predictions) {};
                \foreach \i in {-11,...,11} {
                    \fill<6>[myrect, fill=presentation_orange_shaded] (0.2*\i,4.8) rectangle ++(0.1,0.4);
                }
                \node<6> [] at (0,5) {\small\textsc{predictions}};

                \node<5> [mybox, fill=black!10] at (0,4) (downstream) {\small\textsc{downstream model}};

                \node<4> [mybox, fill=presentation_blue] at (0,3) (text) {};
                \foreach \i in {-11,...,11} {
                    \fill<4>[myrect, fill=presentation_blue_shaded] (0.2*\i,2.8) rectangle ++(0.1,0.4);
                }
                \node<4> [] at (0,3) {\small\textsc{text}};

                \node<3> [mybox, fill=black!10] at (0,2) (recognition) {\small\textsc{speech recognition}};

                \node<2> [mybox, fill=black!10] at (0,1) (representation) {\small\textsc{representation learning}};

                \node<1> [mybox, fill=presentation_green] at (0,0) (speech) {};
                \foreach \i in {-11,...,11} {
                    \fill<1>[myrect, fill=presentation_green_shaded] (0.2*\i,-0.2) rectangle ++(0.1,0.4);
                }
                \node<1> [] at (0,0) {\small\textsc{speech}};

                \node<7> [draw, rectangle, rounded corners, line width=0.15cm, presentation_red, fit=(speech)(representation)(recognition)(text)(predictions), inner sep=10pt] (uncertainty) {};
                \node<7> [above] at (uncertainty.north) {\small\textsc{uncertainty}};
            \end{tikzpicture}
        }
        \end{column}
    \end{columns}
\end{frame}
